Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Space fixes

Consider the following typical situations within a cluster:
\begin{enumerate}
  \item Some clients have regular throughput and flexible deadlines, while some
    clients have hard real-time constraints and variable traffic.
  \item Different tasks make use of different characteristics of hardware on
    machines in the cluster, for example high ratios of RAM to CPU on a
    particular machine, or GPUs or other hardware that is available on only
    certain machines.
  \item Tasks require data which is located on disk or even in memory somewhere
    in the cluster, and co-locating the tasks with the data improves
    performance.
\end{enumerate}

In section~\ref{drawbacks} we show that current implementations
of Mesos do not remain efficient, strategy-proof, envy-free,
or compatible with the sharing incentive under these conditions.
The key problem is that the accept/reject framework is not sufficiently expressive
to allow users to ``honestly'' express their preferences in these cases,
and so it is unsurprising that they are incentivized to engage
in strategic behavior (indeed, they are intended to engage in strategic behavior)
and the results need not be efficient.

@@

A naive representation of this function would use an exponential amount of
space. While we can consider several methods greatly varying in
complexity for encoding this function more compactly, we use the following
two-level representation:
\begin{itemize}
  \item A list of \emph{tasks}, with the assumption that a framework's
    willingness to pay for any set of tasks is simply the total
    willingness to pay for tasks in that set.
  \item For each task a list of possible resources which can be used to perform
    that task, together with a willingness to pay for that set of resources.
\end{itemize}
While this obviously cannot represent all possible $\mathcal{B}$, it still
allows enough flexibility to cover all of the applications we allude to
in the paper---to handle deadlines, inhomogeneous resources, fragmentation,
tasks of differing priorities, and so on.

@@

We will use the suggestive term ``realistic conditions'' to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):

\begin{itemize}
\item Users have time-varying demands and tasks of varying importance.
\item Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
\item Users face deadlines.
\item Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources. Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.
\end{itemize}

We say that a system is ``demand-based'' if it elicits a demand from each user and makes assignments on the basis of the stated demands. For example, DRF, asset allocation, and CEEI all fall into this class.
\vspace{-5mm}
\begin{theorem}\label{demand-bad}
Any demand-based system which is Pareto efficient under realistic conditions must sometimes assign the entire cluster to a single user, an extreme violation of fairness.
\end{theorem}
\vspace{-5mm}
\begin{pproof}
We provide the proof for the time-varying demands case. The other arguments are exactly analogous. We give an extremely simple and artificial case, though analogous behavior would be expected in more realistic cases.

@@

Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences than DRF, resulting in better performance for the market-based mechanism. DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others. By better scheduling jobs on machines that best complete them, we see the overall performance improvements of the market-based mechanism.

>>>>

Consider the following typical situations within a cluster:
\vspace{-5mm}
\begin{enumerate}
\itemsep0em
  \item Some clients have regular throughput and flexible deadlines, while some
    clients have hard real-time constraints and variable traffic.
  \item Different tasks make use of different characteristics of hardware on
    machines in the cluster, for example high ratios of RAM to CPU on a
    particular machine, or GPUs or other hardware that is available on only
    certain machines.
  \item Tasks require data which is located on disk or even in memory somewhere
    in the cluster, and co-locating the tasks with the data improves
    performance.
\end{enumerate}
\vspace{-5mm}
In section~\ref{drawbacks} we show that current implementations
of Mesos do not remain efficient, strategy-proof, envy-free,
or compatible with the sharing incentive under these conditions.
The key problem is that the accept/reject framework is not sufficiently expressive
to allow users to ``honestly'' express their preferences in these cases,
and so it is unsurprising that they are incentivized to engage
in strategic behavior (indeed, they are intended to engage in strategic behavior)
and the results need not be efficient.

@@

A naive representation of this function would use an exponential amount of
space. While we can consider several methods greatly varying in
complexity for encoding this function more compactly, we use the following
two-level representation:
\vspace{-5mm}
\begin{itemize}
\itemsep0em
  \item A list of \emph{tasks}, with the assumption that a framework's
    willingness to pay for any set of tasks is simply the total
    willingness to pay for tasks in that set.
  \item For each task a list of possible resources which can be used to perform
    that task, together with a willingness to pay for that set of resources.
\end{itemize}
\vspace{-5mm}
While this obviously cannot represent all possible $\mathcal{B}$, it still
allows enough flexibility to cover all of the applications we allude to
in the paper---to handle deadlines, inhomogeneous resources, fragmentation,
tasks of differing priorities, and so on.

@@

We will use the suggestive term ``realistic conditions'' to mean a situation in which any of the following occur (i.e., our negative results apply when any of these occur, and the setting is otherwise the simplest setting of static, homogeneous demands for homogeneous resources):
\vspace{-5mm}
\begin{itemize}
\itemsep0em
\item Users have time-varying demands and tasks of varying importance.
\item Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
\item Users face deadlines.
\item Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources. Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.
\end{itemize}
\vspace{-5mm}
We say that a system is ``demand-based'' if it elicits a demand from each user and makes assignments on the basis of the stated demands. For example, DRF, asset allocation, and CEEI all fall into this class.
\vspace{-5mm}
\begin{theorem}\label{demand-bad}
Any demand-based system which is Pareto efficient under realistic conditions must sometimes assign the entire cluster to a single user, an extreme violation of fairness.
\end{theorem}
\vspace{-5mm}
\begin{pproof}
We provide the proof for the time-varying demands case. The other arguments are exactly analogous. We give an extremely simple and artificial case, though analogous behavior would be expected in more realistic cases.

@@

Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences for special resources than DRF, resulting in better performance for the market-based mechanism. DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others.
